High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2021-05-10 Draft_V4046Sgr_mnras.tex
Updates from Overleaf

% Abstract of the paper
\begin{abstract}
    The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.  We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc. The surprisingly thin Ring13 is nonetheless roughly 4 times wider than the model scale height. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by our physical model.
\end{abstract}

@@

Recent observations of young circumstellar discs have transformed current knowledge of planet formation. The focus of resolved imaging with the Atacama Large Millimetre/submillimetre Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}. It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}. The sample is not biased towards exceptionally bright and large discs. The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs. This article on V4046 Sagittarii (Sgr) is part of a companion programme, the DARTTS survey with ALMA (DARTTS-A, Perez et al. {\em in prep}), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.

@@

Disc structures can be explored by means of comparing millimetre continuum and scattered-light images. These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane. By comparing both, is easier to determine whether asymmetries in scattered light correspond to surface ripples or deep structures intrinsic to the underlying density distribution.

From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rosenfeld_2013} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimeter dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass. Later on, \citet{Avenhaus_2018} using DPI in the J and H bands confirmed the double-ring morphology presented by \citet{Rapson_2015}, where the micron-size dust disc presented an $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.

The pursuit of creating high-fidelity parametric simulations that resolve NIR scattered-light and millimeter continuum observations simultaneously is something only few have ventured into \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}. A model that achieves this quest can serve as a convenient sample to interpret real data in terms of a physical model. In this paper we aim to reproduce the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and a new high definition 1.3\,mm continuum ALMA image, as a way to throw light on its complex structure and the processes that are occurring in it.

The observations, including new 1.3\,mm continuum data, are described in Section~\ref{sec:Observations}. The parametric model is presented in Section~\ref{sec:model}, which builds up on the previous models of V4046\,Sgr  \citep{Rosenfeld_2013, Ru_z_Rodr_guez_2019, 2019ApJ...882..160Q}. Our results are discussed in Section~\ref{sec:results} and summarised in Section~\ref{sec:Conclusions}.

\section{Observations} \label{sec:Observations}
\subsection{ALMA}

@@

The ring width can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid. In Fig.~\ref{fig:polarring}) is shown the positions of the obtained centroids and widths over the polar decomposition of the ALMA image. On average, we obtained a FWHM of 2.83$\pm$0.50\,au, and a stellocentric radius of 13.15$\pm$0.26\,au. As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim0\farcs021 \,\times \,\sim0\farcs018$, we see that Ring13 is marginally resolved. After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.56\,au.

In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors. However, very likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation. This is summarised in the second panel of Fig.~\ref{fig:polarring}, where is showing the difference between the Gaussian fitting at each azimuth for both optimization. Both fitted centroids follow a curve almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences might be just a consequence of the pointing error or are they a real notable feature of the disc.

@@

\subsection{SPHERE--IRDIS}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
    \caption{(a) Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24. We trace Ring13 using the centroids (solid line) and width of radial Gaussian fits (blue region between the dotted lines). (b) Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in a), while the blue line is obtained for the inner ring orientation.}
    \label{fig:polarring}
\end{figure}

@@

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep{Dullemond_2012}. The general framework of the parametric model that we used is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}. Through trial and error, we found a set of values for the parameters that correctly fit the available data. The final structure of the parametric model is summarised in  Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the aspect ratio profile.

The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

@@

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \,\left( \frac{r}{r_{\circ}}\right)^{1+\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. In hydrostatical equilibrium dust diffusion and settling are expected to balance each other, leading to a settling factor of $\chi = \sqrt{D_{\rm d}/(D_{\rm d} + St)}$ \citep{Dubrulle1995}. Here, $D_{\rm d}$ is a dimensionless parameter that informs about the level of diffusivity (it is typically assumed to be similar to the level of turbulence for the particle sizes regarded here \citep{2007Icar..192..588Y}. The Stokes number,
\begin{equation}
    {\rm St} := 0.5 \,\pi a \rho_{\rm mat} \, \Sigma_{\rm gas}^{-1}, 
\end{equation}
summarises a particle's dynamical behaviour in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density).. By definition, the gas has no settling, and the small dust grain's settling is negligible. As we do not know the level of diffusivity in the disc (this will be a topic of interest in Section~\ref{sec:results}), nor the exact value of $\Sigma_{\rm gas}$, we infer the scaling factor for large dust, $\chi_{\rm ld}$, from the width of Ring13. In the radial profile this ring is observed two to three times wider in the gas-tracing NIR than in the fluxes received from larger grains by ALMA. The gas and the small dust (sd) grains have no settling, so $\chi_{\mathrm{gas}}$ = $\chi_{\mathrm{sd}}$ = 1. The radial spread of Ring13 appears two to three times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the midplane of the disc), leading to $\chi_{\mathrm{ld}}=0.4$. This is analogous to assuming equal radial and vertical turbulent diffusions.

For the vertical structure, \citet{dOrazi} found flaring angles, i.e. $H/r$, of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is $H_\circ = 2.2$\,au at $r_\circ = 18$\,au. This is summarized in Fig.\ref{fig:profiles} bottom panel that shows the aspect ratio profile $h(r)=H(r)/r$.

We propose a three-ringed structure to reproduce the observations. We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc follows a power-law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. Our model extends from 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec. \ref{subsec:SED}).

We choose to use Gaussian profiles to parametrize Ring5 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.1$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.35$\,au, $\sigma_{\mathrm{Ring13}}=2.1$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{au\,g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6. \times 10^{-1}$\,$\mathrm{au\,g\,cm^{-3}}$\} for both components separately.

For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$:
\begin{equation}
  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r),
\end{equation}
with
\begin{equation}
  \delta_{\mathrm{sd}}(r) =
  \begin{cases}
  0    & r < 18\text{\,au} \\
  4.2\times 10^4 & r > 18\text{\,au}.
  \end{cases}
\end{equation}
The inner edge of Ring24 follows a different profile. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the inner edge and the location of maximum density of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allows us to model a smoother inner edge of the outer ring, with $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring. To be consistent with the theory, Ring5 should have a small large-dust population too, but, as this ring is not visible in the ALMA observation, we added just the right mass to be undetectable by the ALMA observation. We also truncated the profile of large dust grains at 63\,au. It is then defined by the sum of its three components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For Ring5 and Ring13, we choose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.1$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.14$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{au\,g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{au\,g\,cm^{-3}}$. For Ring24 we used a similar profile as for the gas --a power-law function-- but with the difference that, in an effort to recreate the break seen in the outer ring, we choose different values for $\gamma = -3.5$ and $R_c$ = 39\,au between 27.9 and 35.3\,au. The surface density for large dust grains in the outer ring is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma(r)} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  7.2 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
  3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
  2.7 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large\,dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}

>>>>

% Abstract of the paper
\begin{abstract}
    The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring. We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm continuum of V4046\,Sgr which, combined with SPHERE--IRDIS polarized images and well-sampled spectral energy distribution (SED), allow us to propose a physical model using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.15$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 2.46$\pm$0.56\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. Between 25\,au and $\sim$35\,au the brightness of Ring24 is relatively flat and then breaks into a steeper tail that reaches out to $\sim$60\,au. In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$5\,au (Ring5) composed mainly of small dust grains, hiding under the IRDIS coronagraph, and surrounding an inner circumbinary disc. The surprisingly thin Ring13 is nonetheless roughly 4 times wider than its expected vertical extent. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by our physical model.
\end{abstract}

@@

Recent observations of young circumstellar discs have transformed current knowledge of planet formation. The focus of resolved imaging with the Atacama Large Millimeter/submillimeter Array (ALMA) or with the current generation of high-contrast cameras has mainly been towards the brighter sources \citep[e.g.][]{2020ARA&A..58..483A}. It is to address this bias that the programme called ``Discs Around T Tauri Stars with SPHERE'' (DARTTS-S) collected differential polarization imaging (DPI) data secured with the Spectro-Polarimeter High-contrast Exoplanet REsearch \citep[SPHERE][]{2019A&A...631A.155B} in a total of 29 solar-type stars \citep[][]{Avenhaus_2018,Garufi2020}. The sample is not biased towards exceptionally bright and large discs. The DARTTS observations revealed diverse structures and morphologies in the scattering surface of these discs. This article on V4046 Sagittarii (Sgr) is the first installment of a companion programme, the DARTTS survey with ALMA (DARTTS-A), which will present millimetre observations of nine protoplanetary discs previously imaged in polarized scattered light in DARTTS-S.

Disc structures can be explored by means of comparing millimetre continuum and scattered-light images. These observations allow us to see the distribution of different populations of dust particles: while ALMA traces the millimetre-sized grains settled in the mid-plane of the disc, scattered-light imaging accounts for photons reflected off micron-sized dust at the disc surface layer, high above the mid-plane. Therefore, the comparison of both allows to trace the dynamics present at different vertical heights in the disc.

@@

From previous analysis of radio wavelength observations taken with Sub-millimeter Array (SMA) \citep{Rosenfeld_2013} and subsequently with ALMA \citep{Guzman_2017,Huang_2017,Bergner_2018,Kastner_2018}, it was detected that the millimetre dust configuration of the circumbinary disc had a large inner hole of $\sim$30\,au, featuring a narrow ring centred around 37\,au that accounted for most of the dust mass. By using DPI in the J- and H-band, \citet{Avenhaus_2018} confirmed the double-ring morphology previously presented in \citet{Rapson_2015}, where the observed brightness presented a $\sim$10\,au-wide inner cavity, a narrow ring at $\sim$14\,au and the outer ring centred at $\sim$27\,au.

The suggestion of a parametric model that simultaneously fits the NIR scattered-light and millimetre continuum brightness is challenging and has been attempted in only few previous studies \citep[e.g.][]{Dong_2018,2019MNRAS.486..304B, Ru_z_Rodr_guez_2019}. A successful model can serve as a convenient sample to link the observations to the structure of the underlying dust density distribution.

In this paper we present new observations of the continuum emission at 1.3 mm of V4046 Sgr which reveal previously undiscovered structures. This work also aims to reproduce the observations of the protoplanetary disc around V4046\,Sgr with a 3D model using as guidance previous NIR images, the spectral energy distribution (SED) and a new high definition 1.3\,mm continuum ALMA image, as a way to throw light on its complex structure and the processes that are occurring in it.

The details of the observations taken into account are described in Section~\ref{sec:Observations}. The parametric model is presented in Section~\ref{sec:model}, the results are discussed in Section~\ref{sec:results} and in Section~\ref{sec:Conclusions} we present our conclusions.

\section{Observations} \label{sec:Observations}
\subsection{ALMA}  \label{subsec:ALMA}

@@

The ring width can be measured in polar coordinates by fitting 1-D Gaussians at each azimuth, thus obtaining a width and centroid. The top panel of Fig.~\ref{fig:polarring}) shows the positions of the obtained centroids and widths over the polar decomposition of the ALMA image. On average, we obtained a FWHM of 2.83$\pm$0.25\,au, and a stellocentric radius of 13.15$\pm$0.42\,au. As the {\tt uvmem} model image has an approximate {\tt uvmem} beam of $\sim0\farcs021 \,\times \,\sim0\farcs018$, we see that Ring13 is marginally resolved. After subtraction of the {\tt uvmem} beam, the ring width is $\sim$2.46$\pm$0.40\,au.

In a second optimization of the disc orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.86$\pm$0.02\,$\degr$, with an inclination of 33.92$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 2\pm0.02$\,mas $\Delta \delta = 12\pm0.02$\,mas relative to the stars. We see that both Ring13 and Ring24 share a very similar orientation and centre, given the errors. However, very likely due to the joint effect of all these small differences, we can see that there are some hints for a somewhat different orientation. This is summarised in the second panel of Fig.~\ref{fig:polarring}, where it shows the centroids of the Gaussian fitting at each azimuth for both optimization. The curve that follows these fitted centroids for each of the optimizations goes almost entirely within the errors of the other one, leaving the window open to the discussion of if this differences are just a consequence of the pointing error or are they a real notable feature of the disc.

@@

\subsection{SPHERE--IRDIS}  \label{subsec:SPHERE}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{polar_ring_aprox_and_diff_inner.pdf}
    \caption{{\bf (a)} Polar decomposition of the 1.3\,mm continuum image, using the orientation of Ring24. We trace Ring13 using the centroids (solid line) and width of radial Gaussian fits (blue region between the dotted lines). {\bf (b)} Centroid of Ring13, for two disc orientations: the orange line corresponds to the same trace as in (a), while the blue line is obtained for the inner ring orientation.}
    \label{fig:polarring}
\end{figure}

@@

The multi-frequency data can be interpreted in terms of a physical structure using radiative transfer predictions, for which we used the \textsc{radmc3d} package \citep[version 2.0,][]{Dullemond_2012}. The general framework of the parametric model that we developed is similar to that in \citet{2018MNRAS.477.5104C} for DoAr\,44, and the initial model values were inspired from those in \citet{Rosenfeld_2013}, \citet{Ru_z_Rodr_guez_2019} and \citet{2019ApJ...882..160Q}. Computing a high-resolution radiative transfer model that succeeds in the reproduction of multi-frequency imaging and the SED, is finding a solution to a very degenerative problem, so obtaining an ideal model with a full parameter exploration requires a level of computation and time that exceeds our capabilities. Consequently, our approach was to find through trial and error a set of values for the parameters that closely fit the available data. Then, we improved this fit implementing one dimensional chi squared optimizations for some key parameters (more on this in sec.~\ref{sec:results}). The final structure of the parametric model is summarised in Fig.~\ref{fig:profiles}, where we show on the top panel surface density profiles for gas, large and small dust grains, and in the bottom panel the aspect ratio profile.

The stars were modeled using two Kurucz photosphere models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$, respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin. Their PA was set to 250\,$\degr$, so that the secondary lies to the NW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

@@

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \,\left( \frac{r}{r_{\circ}}\right)^{1+\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at $r$ = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. In hydrostatical equilibrium dust diffusion and settling are expected to balance each other, leading to a settling factor of $\chi = \sqrt{D_{\rm d}/(D_{\rm d} + St)}$ \citep{Dubrulle1995}. Here, $D_{\rm d}$ is a dimensionless parameter that informs about the level of diffusivity (it is typically assumed to be similar to the level of turbulence for the particle sizes regarded here \citep{2007Icar..192..588Y}. The Stokes number,
\begin{equation}
    {\rm St} := \frac{1}{2} \,\frac{\pi a \rho_{\rm mat}}{\Sigma_{\rm gas}}, 
\end{equation}
summarises a particle's dynamical behaviour in a given environment (where $\rho_{\rm mat}$ represents a dust particle's material density). By definition, the gas has no settling, and the small dust grains settling is negligible, so that $\chi_{\rm gas}=\chi_{\rm sd}=1$. As we do not know the level of diffusivity in the disc (this will be a topic of interest in Section~\ref{sec:results}), nor the exact value of $\Sigma_{\rm gas}$, we infer the scaling factor for large dust, $\chi_{\rm ld}$, from the width of Ring13. In the radial profile this ring is observed two to three times wider in the gas-tracing NIR than in the fluxes received from larger grains by ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the mid-plane of the disc), leading to $\chi_{\mathrm{ld}}=0.4$. This is analogous to assuming equal radial and vertical turbulent diffusions.

For the vertical structure, \citet{dOrazi} found flaring angles (i.e. height of the ring over the disk midplane divided by the radius of the ring), of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model aims to reproduce those values by using two different flaring indices, $\psi_1$ and $\psi_2$. The separation between the two values was set at $r = 18$\,au with $\psi_1=0.2$ for Ring5 and Ring13, and $\psi_2=0.5$ for Ring24. The scale height is set to $H_\circ = 0.94$\,au at $r_\circ = 18$\,au. This is summarized in bottom panel of Fig.~\ref{fig:profiles} that shows the aspect ratio profile $h(r)=H(r)/r$.

Although both ALMA and SPHERE--IRDIS images display two-ringed morphologies, we propose a three-ringed structure plus an inner disc to reproduce the observations. This bold decision is due the major fit improvement in the SED (more on this in sec.~\ref{sec:results}). We separate the disc into four individual regions: the inner disc, Ring5, Ring13, and Ring24. The combined gas surface density profile is then given by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring5}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc model follows a power-law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density power-law index. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =3.3\times10^{-4}$\,$\mathrm{g\,cm^{-3}}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. Our model extends from 0.3\,au outwards, consistent with the inner edge radius inferred from the SED data (See sec.~\ref{subsec:SED}).

We chose to use Gaussian profiles to parametrize Ring5 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring5}}=5.2$\,au, $\mu_{\mathrm{Ring13}}=14.9$\,au\}, ring widths \{$\sigma_{\mathrm{Ring5}}=0.25$\,au, $\sigma_{\mathrm{Ring13}}=2.2$\,au\}, and normalizations \{$\Sigma_{\circ,\mathrm{Ring5}}=3.3$\,$\mathrm{g\,cm^{-3}}$, $\Sigma_{\circ,\mathrm{Ring13}}=6.0 \times 10^{-1}$\,$\mathrm{g\,cm^{-3}}$\} for both components separately.

For Ring24 we used the same power-law as for the inner disc but scaled by an empirically obtained factor, $\delta_{\mathrm{sd}}(r)$ and by $\epsilon(r)$, a parameter that allows us model a smoother inner edge of the outer ring:
\begin{equation}
  \Sigma_{\mathrm{Ring24}}(r) = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}}(r)\,\epsilon(r),
\end{equation}
with
\begin{equation}
  \delta_{\mathrm{sd}}(r) =
  \begin{cases}
  0    & r < 18\text{\,au} \\
  4.2\times 10^4 & r > 18\text{\,au},
  \end{cases}
\end{equation}
and 
\begin{equation}
    \epsilon(r) = 
    \begin{cases}
  0    & r < R_\mathrm{in} \,\, {\rm and} \,\, R_\mathrm{peak} < r \\
  \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3 & R_\mathrm{in} < r < R_\mathrm{peak},
    \end{cases}
\end{equation}
where $R_\mathrm{in}$ and $R_\mathrm{peak}$ respectively mark the inner edge and the location of maximum density of the outer ring. We used $R_\mathrm{in,gas}$ = 18.0\,au and $R_\mathrm{peak,gas}$ = 26.4\,au.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a larger inner cavity, a larger gap between Ring13 and Ring24, and a break in the outer ring. We only included a low density of large grains within Ring5, just underneath the detection limit of the ALMA observation, as it does not show any visible signature.We also truncated the profile of large dust grains at 63\,au. It is then defined by the sum of its three components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = \Sigma_{\mathrm{Ring5,ld}} + 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For Ring5 and Ring13, we chose Gaussian profiles parameterized with centroid radii $\mu_{\mathrm{Ring5, ld}}=5.2$\,au and $\mu_{\mathrm{Ring13, ld}}=13.22$\,au, ring widths of $\sigma_{\mathrm{Ring5,ld}}=0.1$\,au and $\sigma_{\mathrm{Ring13,ld}}=0.85$\,au, and normalizations $\Sigma_{\circ,\mathrm{Ring5,ld}}=1.3\times10^{-4}\,\mathrm{g\,cm^{-3}}$ and $\Sigma_{\circ,\mathrm{Ring13,ld}}=2.4\,\mathrm{g\,cm^{-3}}$. For Ring24 we used a similar profile as for the gas (a power-law function). The surface density for large dust grains in the outer ring is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}}(r) = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{-\gamma_{\mathrm{ld}}} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}(r)}\right)^{2-\gamma_{\mathrm{ld}}}\right]\,\delta_{\mathrm{ld}}(r) \,\epsilon(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  7.2 \times10^{4} & 24.6 < r < 27.9\text{\,au} \\
  3.2 \times10^{4} & 27.9 < r < 35.3\text{\,au} \\
  2.7 \times10^{5} & 35.3 < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
and for $\epsilon(r)$ we used $R_\mathrm{in,ld}$ = 24.2\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$. In an effort to recreate the break seen in the outer ring, we used
\begin{equation}
  \gamma_{\mathrm{ld}}(r) =
  \begin{cases}
  3.5 & 27.9\text{\,au} < r < 35.3\text{\,au} \\
    1                 &  {\rm elsewhere} \\

  \end{cases}
\end{equation}
